Standardized crypto-loans on\\ the Cardano blockchain

### 2021-04-08 papers/actus2021/article.tex
tidy up

\author{Dmytro Kondratiuk\inst{1} \and
				Pablo {Lamela Seijas}\inst{1}\orcidID{0000-0002-1730-1219} \and
				Alexander Nemish\inst{1} \and
                Simon Thompson\inst{1,2}\orcidID{0000-0002-2350-301X}}

>>>>

\author{Dmytro Kondratiuk\inst{1} \and
				Pablo {Lamela Seijas}\inst{1}\orcidID{0000-0002-1730-1219} \and
				Alexander Nemish\inst{1} \and
                Simon Thompson\thanks{Corresponding author.}\inst{1,2}\orcidID{0000-0002-2350-301X}}
